\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{hyperref}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlength{\parskip}{4pt}

\newcommand{\ressection}[1]{\vspace{6pt}\textbf{\large #1}\\[-2pt]\hrule\vspace{4pt}}

\begin{document}

\begin{center}
    {\LARGE \textbf{Ashar S. Ahmed}} \\
    Software Developer \& Cyber Security Professional \\
    \href{mailto:ashar@aahmed.ca}{ashar@aahmed.ca} \;|\; \href{https://aahmed.ca}{aahmed.ca} \;|\; \href{https://linkedin.com/in/asharsahmed}{linkedin.com/in/asharsahmed} \;|\; \href{https://github.com/asharahmed}{github.com/asharahmed}
\end{center}

\ressection{Summary}
Building secure, scalable solutions for the public sector with experience across Canadian government and healthcare environments.

\ressection{Experience}
\textbf{Cyber Security Advisor} \hfill Jan 2023 -- Present \\ 
Dr. Shariq Mumtaz Medicine Professional Corporation
\begin{itemize}
    \item Initiated corporate security policy to protect confidentiality, integrity, and availability of assets.
    \item Implemented zero-trust via MFA, macOS pilot, and continuous monitoring.
    \item Strategized security measures meeting PHIPA and PIPEDA requirements.
    \item Managed stakeholder communications with updates and best practice recommendations.
\end{itemize}

\textbf{Associate Software Developer} \hfill Oct 2021 -- Jan 2022 \\ 
Canadian Digital Service
\begin{itemize}
    \item Structured artifacts for reliable, accessible support for federal organizations.
    \item Automated workflows using Terraform for AWS cloud environments.
    \item Improved reliability and accessibility using Python and Flask.
\end{itemize}

\textbf{Software Developer} \hfill Feb 2021 -- Oct 2021 \\ 
Innovation, Science and Economic Development Canada
\begin{itemize}
    \item Modernized web apps with micro-services, reducing load times by 65 percent.
    \item Awarded Directors General Award of Merit for exceptional performance.
    \item Developed apps using ES2015 JavaScript to visualize open data.
    \item Streamlined apps with Spin.js and Google Cloud Platform.
    \item Analyzed performance through unit and integration testing.
\end{itemize}

\textbf{Software Developer Intern (Co-op)} \hfill Sep 2020 -- Dec 2020 \\ 
National Research Council of Canada
\begin{itemize}
    \item Developed Oracle Platform apps using HTML5, JavaScript, and CSS.
    \item Maintained Oracle SQL database with PL/SQL scripts for CRUD operations.
    \item Integrated web apps with CMS to streamline information accessibility.
\end{itemize}

\textbf{Call Centre Agent Intern (FSWEP)} \hfill Jul 2020 -- Sep 2020 \\ 
Employment and Social Development Canada
\begin{itemize}
    \item Assisted Canadians with CERB inquiries during the COVID-19 pandemic.
\end{itemize}

\ressection{Education}
\textbf{Master of Public Administration} \hfill Jan 2025 -- Present \\ 
University of Birmingham

\textbf{Master of Science in Cyber Security and Information Assurance} \hfill Issued 2024 \\ 
Western Governors University

\textbf{Bachelor of Computer Science} \hfill Issued 2024 \\ 
Dalhousie University

\ressection{Certifications}
\begin{itemize}
    \item CompTIA CySA+ (2024)
    \item CompTIA PenTest+ (2024)
    \item Zero-Trust Certificate, Cloud Security Alliance (2023)
    \item Systems Security Certified Professional, ISC2 (2022)
    \item Certified in Cybersecurity, ISC2 (2022)
    \item AWS Certified Developer - Associate (2022)
    \item AWS Certified Solutions Architect - Associate (2022)
\end{itemize}

\ressection{Skills}
\textbf{Languages:} JavaScript, TypeScript, Python, Java, PHP, SQL, PL/SQL, HTML/CSS \\ 
\textbf{Cloud \& DevOps:} AWS EC2, AWS S3, DynamoDB, Terraform, GCP \\ 
\textbf{Tools:} Git, Bash, Linux, Node.js, Flask, Oracle DB \\ 
\textbf{Practices:} Agile/Scrum, Zero-Trust, A11Y, Data Engineering, Testing

\ressection{Publications}
The Cyber Centre and Its Technologies - An Analysis. \textit{Canadian Military Journal}. November 2022.

\end{document}
